Supplementary material to ``Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data''

### 2015-07-06 Correspondence/revisions.tex
finished responding to reviewer 2's comments. Closes #27, closes #28, closes #37

 \item [Reviewer 2:] \textbf{Minor comments:} Fixed typo in the abstract; 
 \begin{enumerate}
  \item 
 \end{enumerate}

>>>>

 \item [Reviewer 2:] \textbf{Minor comments:} Fixed typo in the abstract; Added 
text to the discussion stating that we expect the effects of underreporting to 
cancel out in the calculation of the Attack ratio. 
 \begin{enumerate}
  \item Reference 5, despite having similar concepts as those discussed in our 
paper, has quite different goals. we have however, cited another publication 
(ref 26), which fro the same group and based on the same field study, and use 
their findings about seroprevalence in the 'results and discussion' section.
\item We have not found articles combining the use of aggregated data to study 
variable force of infection, however we have reviewed other works modeling 
variable FoI (refs 7, 8, 9, 10, 12).
 \end{enumerate}
